### 2019-11-22 1_introduction.tex
Edits.

Using Task Bench we were able to quickly incorporate 15 very different parallel and distributed
programming systems.  By running all systems on common benchmarks we were able to quantify phenomena
that have never before been measured.
Most strikingly, the overheads of the systems we examine vary by more than five orders
of magnitude, with popular, widely used systems at both ends of the spectrum!  Clearly
the slower systems have ``good enough'' performance for some class of applications, while presumably
providing advantages in programmer productivity.

@@

We conduct a comprehensive comparative study of Task Bench
implementations in 15 programming systems
listed in Section~\ref{sec:implementation}.
%% :
%% Chapel \cite{Chapel15}, Charm++ \cite{Charmpp93}, Dask \cite{Dask15}, MPI \cite{MPI}, MPI+X (OpenMP, CUDA),
%% OmpSs \cite{OmpSs11}, OpenMP \cite{OpenMPSpec40},
%% PaRSEC \cite{PARSEC13}, Realm \cite{Realm14}, Regent \cite{Regent15},
%% Spark \cite{Spark10}, StarPU \cite{StarPU11},
%% Swift/T \cite{Wozniak13}, TensorFlow \cite{TensorFlow15}, and
%% X10 \cite{X1005}.
Using METG, we find that a number of factors---node
count, accelerators, and complex dependencies, among
others---individually or in combination contribute to an order of
magnitude or greater increase in METG, even in the most efficient
systems. While some systems can achieve sub-microsecond METG(50\%) in
best-case scenarios, we show that a more realistic
bound for running nearly any application at scale is 100~\textmu{}s with
current technologies. Our study includes several asynchronous systems
which are designed to provide benefits such as overlapped computation
and communication. While small-scale benchmarks of these systems
suffer from increased overhead, we find that the benefits of these systems become
tangible at scale (provided the runtime overhead doesn't increase
beyond about 100~\textmu{}s).

@@

%% We find asynchronous systems can provide benefits
%% (e.g., overlapping compute and communication), but only if system overheads do not exceed roughly
%% 100~\textmu{}s.

%% This implies that simplifying the application space too much
%% (e.g., by using trivial dependencies) risks overemphasizing the
%% importance of the lightweight mechanisms in such systems---a risk that
%% can be mitigated by using Task Bench's more complete coverage of the
%% space of application scenarios.

\zap{
Using METG, we determine the baseline
runtime overhead of each system along with overheads associated with
increasing numbers of and/or variations in the pattern of dependencies. We
also explore each system's ability to scale, hide communication
overhead, and mitigate load imbalance.
} % zap

@@

During the development of Task Bench, we have identified performance
bugs in five systems: Chapel, Dask, PaRSEC, Realm and
TensorFlow. Three have been (or are being) fixed and the others have
been acknowledged by the developers of the respective systems. In some
cases these correspond to order of magnitude (or even asymptotic)
improvements in the performance of the underlying systems---benefits
which apply well beyond Task Bench to all classes of applications.

The paper is organized as follows: Section~\ref{sec:task-bench}
describes the Task Bench design. Section~\ref{sec:implementation}
discusses implementations in 15 systems.  Section~\ref{sec:metg}
defines METG and its relationship to quantities of interest to
application developers.  Section~\ref{sec:evaluation} provides a
comprehensive evaluation on the Cori
supercomputer~\cite{Cori}. Section~\ref{sec:related-work} relates to
previous efforts; Section~\ref{sec:conclusion} concludes.

>>>>

This approach has allowed us to incorporate 15 very different parallel
and distributed programming systems (listed in
Table~\ref{tab:systems}).  By running all systems on common benchmarks
we were able to quantify phenomena
that have never before been measured.
Most strikingly, the overheads of the systems we examine vary by more than five orders
of magnitude, with popular, widely used systems at both ends of the spectrum!  Clearly
the slower systems have ``good enough'' performance for some class of applications, while presumably
providing advantages in programmer productivity.

@@

We conduct a comprehensive study of all 15 Task Bench implementations on
up to 256 Haswell nodes of the Cori supercomputer~\cite{Cori}.
%% :
%% Chapel \cite{Chapel15}, Charm++ \cite{Charmpp93}, Dask \cite{Dask15}, MPI \cite{MPI}, MPI+X (OpenMP, CUDA),
%% OmpSs \cite{OmpSs11}, OpenMP \cite{OpenMPSpec40},
%% PaRSEC \cite{PARSEC13}, Realm \cite{Realm14}, Regent \cite{Regent15},
%% Spark \cite{Spark10}, StarPU \cite{StarPU11},
%% Swift/T \cite{Wozniak13}, TensorFlow \cite{TensorFlow15}, and
%% X10 \cite{X1005}.
Using METG, we find that a number of factors---node
count, accelerators, and complex dependencies, among
others---individually or in combination contribute to an order of
magnitude or greater increase in METG, even in the most efficient
systems. While some systems can achieve sub-microsecond METG(50\%) in
best-case scenarios, we show that a more realistic
bound for running nearly any application at scale is 100~\textmu{}s with
current technologies. Our study includes several asynchronous systems
which are designed to provide benefits such as overlapped computation
and communication. While small-scale benchmarks of these systems
suffer from increased overhead, we find that the benefits of these systems become
tangible at scale (provided the runtime overhead doesn't increase
beyond about 100~\textmu{}s).

@@

@@

Beyond comparative study, the ability to explore a large configuration
space also enables the discovery of bugs in the underlying systems. We
found five performance issues, ranging from communication efficiency
(Chapel, Realm), to the efficiency of task pruning, analysis and
constant folding (PaRSEC, Dask and TensorFlow). Three have been fixed
and all have been acknowledged by the developers of the respective
systems. (All were either fixed or worked around in our experiments.)
In some cases these correspond to order of magnitude (or even
asymptotic) improvements in the performance of the underlying
systems---benefits which apply well beyond Task Bench to all classes
of applications.

The paper is organized as follows: Section~\ref{sec:task-bench}
describes the Task Bench design. Section~\ref{sec:implementation}
discusses implementations in 15 systems.  Section~\ref{sec:metg}
defines METG and its relationship to quantities of interest to
application developers.  Section~\ref{sec:evaluation} provides a
comprehensive evaluation on Cori. Section~\ref{sec:related-work} relates to
previous efforts; Section~\ref{sec:conclusion} concludes.
